InnoDB Full text Search hacking with Shiny/R

### 2015-12-28 article.rmd
change on the string conn
Added comments
Clean some testing code

#Comment if you want to avoid reload all the data
#source('~/fts_article/load.R')

@@

                DataResults = reactive({
                   f<-function(x) {as.character(input$filtering)}
                  sql <- paste("SELECT * FROM bookContentByLine WHERE MATCH(content) AGAINST(\"" ,f(x)," \" ",input$ftsMode,") ", sep = "")

                  rs <- head(dbGetQuery(con, sql), 50)
                  return(rs)

>>>>

# Comment if you want to avoid reload all the data
# If you want to start from scratch, uncomment the following line.
# Otherwise, you can restore the dumps located in the dumps folder
#source('~/fts_article/load.R')

@@

                DataResults = reactive({
                   f<-function(x) {as.character(input$filtering)}
                  sql <- paste("SELECT FTS_DOC_ID, bookid, 
                              MATCH(content) AGAINST(\"" ,f(x)," \" ",input$ftsMode,"), content 
                              FROM bookContentByLine WHERE MATCH(content) AGAINST(\"" ,f(x)," \" ",input$ftsMode,") LIMIT 50", sep = "")
